Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-26 Scripts/Initial_Analysis.Rmd
save data for plotting
fixed bug

taxon_list <- c(600015,600017)
taxons <- c(600004,600004,600015,600017)
x <- NULL
x <- PropChange(taxons)

@@

@@

# clean names for function
taxon_list <- gsub(".*_","",taxon_list) 
taxon_list <- gsub("\\..*","",species_list)

Restuls <- PropChange(taxon_list)

>>>>

@@

 return(proportion_change)

@@

# clean names for function
taxon_list <- gsub(".*_","",taxon_list) 
taxon_list <- gsub("\\..*","",taxon_list)

Restuls <- PropChange(taxon_list[1:2])

write.csv(Results,
          "Clean_Results.csv")
